The paper on \Large \bf Blockchain Frontrunning

### 2018-09-10 frontrunning/Latex/sections/paper.tex
[frontrunning] minor edits

Loopring is an open protocol proposed by Wang~\etal to build decentralized exchanges~\cite{wang2018loopring}. This protocol operates a hybrid model with off-chain order management and communication and merely the order matching takes place on the chain. Using Loopring functionality, the users do not need to host their assets on the exchange and and instead they keep their assets in their blockchain wallet. For example, if a user A wants to exchange \emph{token A } to \emph{token B}, she keeps \emph{token A }  safe in her wallet and the Loopring protocol automatically broadcasts the order to the network after user's authorization. If user B wants to exchange, there would be match making miners on the Loopring protocol who matches the orders and swaps the tokens through a smart contract. To solve the front-running issue within the decentralized exchanges, Loopring protocol proposes \emph{dual-authoring} scheme. This solution set two levels of authorization for orders - one for settlement, and one for order matching. In summary, in this scheme a wallet generates a pair of public key (auth-address) and private key (auth-key) for the user, these keys are different from the user's address and its corresponding private key. The address of order's owner, order parameters, and the auth-address are hashed. The hash value, which is called the order-hashed then is signed using the owner's private key. The signature of the ring-hash together with the auth-key are sent to the  miner for matching. In this stage, orders are added to various rings; 
?each ring encapsulates all the fields and data of its containing orders (a ring can have 2 to 10 orders). Once a ring is established, the ring miner uses each order's auth-key to sign the hash of the ring, together with his own address, and the mining parameters. He also needs to sign the hash of the ring together with the mining parameters using his own private key. The miner then sends all the signatures to the Loopring smart contract (LPSC). Eventually, the Loopring protocol verifies each signatures against their corresponding auth-key of each order and does not accept the ring if the signatures are not valid. Doing so, it is assured that (i) the orders are be modified (because they are signed using the owner's private key), (ii) no other miner can mine the ring (because the miner's address is signed using his private key), and no user can front-run the orders within the ring (because other users do not have access to the auth-keys and hence are not able to generate new transactions with auth-keys signatures on them).

>>>>

Loopring is an open protocol proposed by Wang~\etal to build decentralized exchanges~\cite{wang2018loopring}. This protocol operates a hybrid model with off-chain order management and communication and merely the order matching takes place on the chain. Using Loopring functionality, the users do not need to host their assets on the exchange and instead they keep their assets in their blockchain wallet. For example, if user A wants to exchange \emph{token A} with \emph{token B}, she keeps \emph{token A}  safe in her wallet and the Loopring protocol automatically broadcasts the order to the network after user's authorization. If user B wants to exchange, there would be match making miners on the Loopring protocol who matches the orders and swaps the tokens through a smart contract. To solve the front-running issue within the decentralized exchanges, Loopring protocol proposes \emph{dual-authoring} scheme. This solution set two levels of authorization for orders - one for settlement, and one for order matching. In summary, in this scheme a wallet generates a pair of public key (auth-address) and private key (auth-key) for the user, these keys are different from the user's address and its corresponding private key. The address of order's owner, order parameters, and the auth-address are hashed. The hash value, which is called the order-hashed then is signed using the owner's private key. The signature of the ring-hash together with the auth-key are sent to the  miner for matching. In this stage, orders are added to various rings; 
?each ring encapsulates all the fields and data of its containing orders (a ring can have 2 to 10 orders). Once a ring is established, the ring miner uses each order's auth-key to sign the hash of the ring, together with his own address, and the mining parameters. He also needs to sign the hash of the ring together with the mining parameters using his own private key. The miner then sends all the signatures to the Loopring smart contract (LPSC). Eventually, the Loopring protocol verifies each signatures against their corresponding auth-key of each order and does not accept the ring if the signatures are not valid. Doing so, it is assured that (i) the orders are be modified (because they are signed using the owner's private key), (ii) no other miner can mine the ring (because the miner's address is signed using his private key), and no user can front-run the orders within the ring (because other users do not have access to the auth-keys and hence are not able to generate new transactions with auth-keys signatures on them).
